checkData

### 2023-08-24 analysis/checkData.Rmd
Update checkData.Rmd

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)
```

@@

```{r}
d_journals <- d_journals %>%
  select(coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "), 
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
d_journals <- d_journals %>% 
  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
  mutate(sampleID = case_when(
    sample_journal_both == "both" ~ "both",
    sample_journal_both == "na" ~ sample_journal_prominent,
    TRUE ~ sample_journal_both
  )) %>%
  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))

Check entries to ensure secondary coding and identify anomalous entries
```{r}
d_journals %>% 
  count(journal) %>%
  filter(n > 2)
```

```{r}
d_journals %>% filter(`Journal Name` == "CLINICAL PSYCHOLOGY-SCIENCE AND PRACTICE")
```

>>>>

# list of journals in prominent sample
journal_list_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv')) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`)

# list of all prominent journals (some not in sample)
journal_list_prominent_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'))

# list of all random journals (some not in sample)
journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'))
```

@@

```{r}
d_journals <- d_journals %>%
  select(timestamps = Timestamp,
         coder_id = `Coder's Initials`,
         pilot = `Are you piloting?`,
         journal = `Journal Name`,
         journal_empirical = `Does the journal publish empirical research?`,
         anyPPC = `Check the article types page and check for web comments — does the journal offer any type of PPC?`,
         ppc_name_A = `A. Enter the name of the PPC type offered by the journal:`,
         ppc_name_B = `B. Enter the name of the PPC type offered by the journal:`,
         ppc_name_C = `C. Enter the name of the PPC type offered by the journal:`,
         ppc_description_A = `A. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_B = `B. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_description_C = `C. Enter the verbatim description of this type of PPC provided by the journal`,
         ppc_length_A = `A. Are there any length limits for this type of PPC?`,
         ppc_length_B = `B. Are there any length limits for this type of PPC?`,
         ppc_length_C = `C. Are there any length limits for this type of PPC?`,
         ppc_time_A = `A. Are there any time limits for submission of this type of PPC?`,
         ppc_time_B = `B. Are there any time limits for submission of this type of PPC?`,
         ppc_time_C = `C. Are there any time limits for submission of this type of PPC?`,
         ppc_ref_A = `A. Are there any reference limits for this type of PPC?`,
         ppc_ref_B = `B. Are there any reference limits for this type of PPC?`,
         ppc_ref_C = `C. Are there any reference limits for this type of PPC?`,
         ppc_review_A = `A. Is this type of PPC sent for independent external peer review?`,
         ppc_review_B = `B. Is this type of PPC sent for independent external peer review?`,
         ppc_review_C = `C. Is this type of PPC sent for independent external peer review?`,
         ppc_note_A = `A. Anything additional, unusual, or interesting to note?`,
         ppc_note_B = `B. Anything additional, unusual, or interesting to note?`,
         ppc_note_C = `C. Anything additional, unusual, or interesting to note?`,
         general_note = `Anything additional, unusual, or interesting to note?`,
         -starts_with("D. "), 
         -ends_with("Are there any other types of PPC in this journal? (Remember to check for web comments!)`"))

@@

#Creates sampleID column denoting; prominent, random, or both to replace the 4 specified columns above
d_journals <- d_journals %>% 
  mutate(sample_journal_prominent = ifelse(sample_journal_prominent, "prominent", "random")) %>%
  mutate(sample_journal_both = ifelse(sample_journal_both, "both", "na")) %>%
  mutate(sampleID = case_when(
    sample_journal_both == "both" ~ "both",
    sample_journal_both == "na" ~ sample_journal_prominent,
    TRUE ~ sample_journal_both
  )) %>%
  select(-c(sample_journal_prominent, sample_journal_random, sample_journal_both, sample_journal_error))
```

Get JIFs for journals

```{r}
d_journals_prominent <- d_journals %>%
  filter(sampleID %in% c('prominent', 'both'))

d_journals_random <- d_journals %>%
  filter(sampleID == 'random')

journal_list_prominent_all <- journal_list_prominent_all %>% 
  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)

d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

journal_list_random_all <- journal_list_random_all %>%
  select(journal = Journal, WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')

journal_list_prominent_all <- journal_list_prominent_all %>%
  select(-WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')

tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
```

Check journals where we have more than 2 entries

```{r}
d_journals_prominent %>% 
  count(journal) %>%
  filter(n > 2)
```

For the journal HUMAN ARENAS, RTT coded twice, first entry was an error and needs to be removed.
```{r}
d_journals_random <- d_journals_random %>%
  filter(!(journal == "HUMAN ARENAS" & timestamps == "8/6/2023 3:37:26"))
```

For the journal INFANTS & YOUNG CHILDREN, MN coded twice, first entry was an error and needs to be removed.
```{r}
d_journals_random <- d_journals_random %>%
  filter(!(journal == "INFANTS & YOUNG CHILDREN" & timestamps == "7/15/2023 18:51:15"))
```
For the journal EDUCATIONAL PSYCHOLOGIST, AW coded twice, first entry was an error and needs to be removed.
```{r}
d_journals_prominent <- d_journals_prominent %>%
  filter(!(journal == "EDUCATIONAL PSYCHOLOGIST" & timestamps == "6/29/2023 14:06:13"))
```

For the journal EUROPEAN JOURNAL OF PERSONALITY, journal is in both samples so AW coded twice, entries are substantively the same, removing first entry.

```{r}
d_journals_prominent <- d_journals_prominent %>%
  filter(!(journal == "EUROPEAN JOURNAL OF PERSONALITY" & timestamps == "6/29/2023 22:01:35"))
```
For the journal PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW, two entries from NM, first entry was an error.

```{r}
d_journals_prominent <- d_journals_prominent %>%
  filter(!(journal == "PERSONALITY AND SOCIAL PSYCHOLOGY REVIEW" & timestamps == "7/3/2023 18:34:38"))
```

For the journal PSYCHOLOGICAL MEDICINE, two entries from RTT, first entry was an error.

```{r}
d_journals_prominent <- d_journals_prominent %>%
  filter(!(journal == "PSYCHOLOGICAL MEDICINE" & timestamps == "8/6/2023 9:49:10"))
```
